Survivable Set Connectivity

### 2015-05-13 draft.tex
aprpoximate nphard and remove claim but notprove

Unfortunately, solving exact Survivable Set Connectivity is $\mathsf{NP}$-hard \cite{ssc}. Therefore, the focus of this paper is on an approximate solution to a relaxation of this problem given in \cite{ssc}. Instead of requiring at least $k$ edge-disjoint paths between each pair, we require that each pair have at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths, where $n = |V|$. With this relaxation, it is possible to find a subgraph with cost $O(polylog(n))$ times the optimum.

@@

The objective function $\sum c(x) x_e$ simply minimizes the cost of all edges included in $H$. The constraint ensures that for all pairs $(S_i,T_i)$, any cut where $S_i$ is on one side of the cut and $T_i$ is on the other side has at least $k$ edges crossing the cut. We claim (but do not prove) that this property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$.

>>>>

Unfortunately, even approximating Survivable Set Connectivity is $\mathsf{NP}$-hard \cite{ssc}. Therefore, the focus of this paper is on an approximate solution to a relaxation of this problem given in \cite{ssc}. Instead of requiring at least $k$ edge-disjoint paths between each pair, we require that each pair have at least $\Omega(\frac{k}{\log n})$ edge-disjoint paths, where $n = |V|$. With this relaxation, it is possible to find a subgraph with cost $O(polylog(n))$ times the optimum.

@@

The objective function $\sum c(x) x_e$ simply minimizes the cost of all edges included in $H$. The constraint ensures that for all pairs $(S_i,T_i)$, any cut where $S_i$ is on one side of the cut and $T_i$ is on the other side has at least $k$ edges crossing the cut. This property holds if and only if there are $k$ edge disjoint paths from $S_i$ to $T_i$.
